Who we are affects how we vote

### 2019-05-06 elections_conversation.Rmd
Updating on train

---
title: "Who we are affects how we vote"
author: Rob J Hyndman and Di Cook
toc: false
bibliography: references.bib
biblio-style: authoryear-comp
fontsize: 12pt
papersize: a4
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: conversation_preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.pos = "h",
  fig.align = "center",
  cache = TRUE,
  message = FALSE
)
library(tidyverse)
library(eechidna)
library(forcats)
library(ggthemes)
library(knitr)
library(nlme)
library(rgeos)
library(spdep)
library(patchwork)
#library(gridExtra)
#library(grid)
library(predictmeans)
source("functions.R")
source("wrangle.R")
```

@@

It is also interesing to see how this might have changed over time. For example, if wealth was a good predictor of voting patterns in the 2001 election, is it still a good predictor in 2019? Australia has changed in many ways over the last two decades. Rising house prices, country-wide improvements in education, an ageing population, and a decline in religious affiliation, are just some of the ways we have changed. At the same time, political power has moved back and forth between the two major parties. How much can we attribute changes in political power to changes in who we are?

@@

ggplot(timeline, aes(x = year_vis, y = measure)) +
  geom_point(aes(color = as.factor(event), shape = as.factor(event)), size = 4) +
  labs(color = "Event", shape = "Event", x = "Year") +
  geom_hline(yintercept = 0, size = 1, color = "grey", show.legend = FALSE) +
  geom_segment(x = 2001, xend = 2001, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2004, xend = 2004, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2007, xend = 2007, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2010, xend = 2010, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2013, xend = 2013, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2016, xend = 2016, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2001.1, xend = 2001.1, y = 1.4, yend = 0, color = "#F8766D") +
  geom_segment(x = 2006.1, xend = 2006.1, y = 1.4, yend = 0, color = "#F8766D") +
  geom_segment(x = 2011.1, xend = 2011.1, y = 1.4, yend = 0, color = "#F8766D") +
  geom_segment(x = 2016.1, xend = 2016.1, y = 1.4, yend = 0, color = "#F8766D") +
  theme(
    text = element_text(size = 10),
    axis.text.x = element_text(size = 6),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    plot.background = element_blank(),
    axis.ticks.y = element_blank(),
    panel.background = element_blank()
  ) +
  scale_x_discrete(limits = c(2001:2016)) +
  coord_fixed(ratio = 2)
```

@@

Many of the socio-demographic variables have changing scales over the years. For example, inflation-adjusted median rental prices increased across almost all electorates, with median rent of 200 dollars per week placing an electorate in the 90th percentile in 2001, but only the 30th percentile in 2016. In order for socio-demographic effects to be comparable across years, all explanatory variables are standardized so they are comparable across years. By standardizing, each variable is reported as a relative measure compared to all other electorates in the same year.

There are dozens of socio-demographic variables available in the Censuses, with many variables representing similar information about an electorate. So we combined some variables to avoid redundant information. For example, our "Incomes" variable is a combination of median personal income, household income and family income. In this way, we reduced the data set to include 30 socio-demographic variables, listed below.

 * "AusCitizen"
 * "BornAsia"
 * "Born_MidEast"
 * "BornSEEuro"
 * "Born_UK"
 * "BornElsewhere"
 * "Buddhism"
 * "Christianity"
 * "CurrentlyStudying"
 * "DeFacto"
 * "DiffAddress"
 * "Distributive"
 * "Education"
 * "Extractive"
 * "FamHouseSize"
 * "Incomes"
 * "Indigenous"
 * "Islam"
 * "Judaism"
 * "ManagerAdmin"
 * "Married"
 * "MedianAge"
 * "NoReligion"
 * "OneParentHouse"
 * "OtherLanguage"
 * "PropertyOwned"
 * "RentLoanPrice"
 * "SocialServ"
 * "Transformative"
 * "Unemployment"

Each election was modelled separately, to allow us to see any changes over time, and to account for changing electorate boundaries.

@@

```{r plotintercept, fig.cap = "Estimated intercept for each election, which represents the two-party preferred vote for an electorate with mean characteristics.", out.height="20%", out.extra = ''}
intercept_df <- bind_rows(
  data.frame(summary(glsmod16)$tTable)[1, ] %>% mutate(year = "2016"),
  data.frame(summary(glsmod13)$tTable)[1, ] %>% mutate(year = "2013"),
  data.frame(summary(glsmod10)$tTable)[1, ] %>% mutate(year = "2010"),
  data.frame(summary(glsmod07)$tTable)[1, ] %>% mutate(year = "2007"),
  data.frame(summary(glsmod04)$tTable)[1, ] %>% mutate(year = "2004"),
  data.frame(summary(glsmod01)$tTable)[1, ] %>% mutate(year = "2001")
) %>%
  rename(se = `Std.Error`, estimate = Value, p = `p.value`) %>%
  mutate(upper95 = estimate + 1.96 * se, lower95 = estimate - 1.96 * se)

intercept_df %>%
  ggplot() +
  geom_point(aes(x = year, y = estimate), size = 3) +
  geom_linerange(aes(x = year, ymin = lower95, ymax = upper95), size = 1.2) +
  geom_hline(aes(yintercept = 50), alpha = 0.5, size = 1) +
  labs(x = "Election year", y = "Estimate of intercept") +
  guides(col = FALSE) +
  coord_fixed(ratio = 0.2) +
  lims(y = c(45, 55)) +
  theme_bw()
```

Since all socio-demographics have been standardized to have a mean of zero and a variance of one, the intercept in each model can be interpreted as the estimated two-party preferred vote for an electorate with mean characteristics[^3]. Figure \@ref(fig:plotintercept) shows that the baseline of party preference has varied over the elections, with the biggest swing occurring in the 2007 election where the mean electorate shifted more than five percentage points in favour of the Labor party.

[^3]: Mean of all variables aside from Judaism, Indigenous, Islam and Buddhism, where it assumes the mean of the log value.

@@

```{r prepplot, echo = FALSE}
p1 <- grid_visreg("Extractive", top = TRUE)
p2 <- grid_visreg("DiffAddress")
p3 <- grid_visreg("ManagerAdmin")
p4 <- grid_visreg("Transformative")
p5 <- grid_visreg("Incomes")
p6 <- grid_visreg("Unemployment")

p7 <- grid_visreg("MedianAge", top = TRUE)
p8 <- grid_visreg("Judaism")
p9 <- grid_visreg("OtherLanguage")
temp <- grid_visreg("OtherLanguage")
p10 <- grid_visreg("BornAsia")
p11 <- grid_visreg("Education")
p12 <- grid_visreg("BornSEEuro")
p13 <- grid_visreg("DeFacto")
```

```{r partresplot1, fig.cap = "Partial residual plots by election year for a selection of predictors. Linear model with 95\\% confidence bands overlaid. Most predictors have a positive relationship: the larger the value the more likely the electorate preferences the Coalition. The relationship is relatively robust over time, with the exception of Unemployment.", fig.height = 8.5, fig.width = 6, warning = FALSE, fig.pos = 'h'}
(p1 / p2 / (p3 + ylab("Two-party preferred vote (%)                     ")) / p4 / p5 / p6)
```

```{r partresplot2, fig.cap = "Partial residual plots by election year for a selection of predictors. Linear model with 95\\% confidence bands overlaid. Several predictors have a negative relationship: with larger values indicating the electorate more likely preferences Labor. Most relationships are relatively stable over elections, except OtherLanguage and Education.", fig.height = 8.5,  fig.width = 6, warning = FALSE, fig.pos = 'h'}
(p7 / p8 / (p9 + ylab("Two-party preferred vote (%)                     ")) / p10 / p11 / p12 / p13)
```

@@

### A note on similar variables

Many of the Census variables represent similar information, which is why factors were created and some variables were removed. However, some variables remain which are closely related. For example, an electorate's income level (via `Incomes`) is likely to be related to electoral unemployment and labor force participation (via `Unemployment`). In 2001, the coefficient estimate for `Unemployment` is negative but not significant, whilst the `Incomes` variables is significant. If the `Incomes` variable is removed from the model in 2001, `Unemployment` absorbs the negative effect, becoming significant ($p = 0.0056$).

```{r removeunemp, eval = FALSE}
unemp01 <- my_fgls(full_formula,
  my_data = model_df %>% filter(year == "2001") %>% dplyr::select(-Incomes),
  sp_weights = sp_weights_01
)

summary(unemp01)$tTable["Unemployment",]
```

@@

>>>>

---
title: "Who we are affects how we vote"
author: Rob J Hyndman and Di Cook
toc: false
bibliography: references.bib
biblio-style: authoryear-comp
fontsize: 11pt
papersize: a4
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: conversation_preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.pos = "H",
  fig.align = "center",
  cache = TRUE,
  message = FALSE
)
library(tidyverse)
library(eechidna)
library(forcats)
#library(ggthemes)
library(knitr)
library(nlme)
library(rgeos)
library(spdep)
#library(patchwork)
#library(gridExtra)
#library(grid)
library(predictmeans)
source("functions.R")
source("wrangle.R")
```

@@

It is also interesting to see how this might have changed over time. For example, if wealth was a good predictor of voting patterns in the 2001 election, is it still a good predictor in 2019? Australia has changed in many ways over the last two decades. Rising house prices, country-wide improvements in education, an ageing population, and a decline in religious affiliation, are just some of the ways we have changed. At the same time, political power has moved back and forth between the two major parties. How much can we attribute changes in political power to changes in who we are?

@@

ggplot(timeline, aes(x = year_vis, y = measure)) +
  geom_point(aes(color = as.factor(event), shape = as.factor(event)), size = 4) +
  labs(color = "Event", shape = "Event", x = "Year") +
  geom_hline(yintercept = 0, size = 1, color = "grey", show.legend = FALSE) +
  geom_segment(x = 2001, xend = 2001, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2004, xend = 2004, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2007, xend = 2007, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2010, xend = 2010, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2013, xend = 2013, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2016, xend = 2016, y = 1, yend = 0, color = "#00BFC4") +
  geom_segment(x = 2001.1, xend = 2001.1, y = 1.4, yend = 0, color = "#F8766D") +
  geom_segment(x = 2006.1, xend = 2006.1, y = 1.4, yend = 0, color = "#F8766D") +
  geom_segment(x = 2011.1, xend = 2011.1, y = 1.4, yend = 0, color = "#F8766D") +
  geom_segment(x = 2016.1, xend = 2016.1, y = 1.4, yend = 0, color = "#F8766D") +
  scale_x_discrete(limits = c(2001:2016)) +
  coord_fixed(ratio = 2)
```

@@

Many of the socio-demographic variables have changing scales over the years. For example, inflation-adjusted median rental prices increased across almost all electorates, with median rent of 200 dollars per week placing an electorate in the 90th percentile in 2001, but only the 30th percentile in 2016. In order for socio-demographic effects to be comparable across years, all socio-demographic variables were standardized.

There are dozens of socio-demographic variables available in the Censuses, with many variables representing similar information about an electorate. So we combined some variables to avoid redundant information. For example, our "Incomes" variable is a combination of median personal income, household income and family income.

Each election was modelled separately, to allow us to see any changes over time, and to account for changing electorate boundaries. In this article, we highlight the variables with the strongest relationship to the two-party preferred vote, or which have had substantial changes over time. The full analysis is available at https://robjhyndman.com/publications/elections/.

@@

```{r plotintercept, fig.cap = "Estimated intercept for each election, which represents the two-party preferred vote for an electorate with average characteristics.", fig.pos="H"}
intercept_df <- bind_rows(
  data.frame(summary(glsmod16)$tTable)[1, ] %>% mutate(year = "2016"),
  data.frame(summary(glsmod13)$tTable)[1, ] %>% mutate(year = "2013"),
  data.frame(summary(glsmod10)$tTable)[1, ] %>% mutate(year = "2010"),
  data.frame(summary(glsmod07)$tTable)[1, ] %>% mutate(year = "2007"),
  data.frame(summary(glsmod04)$tTable)[1, ] %>% mutate(year = "2004"),
  data.frame(summary(glsmod01)$tTable)[1, ] %>% mutate(year = "2001")
) %>%
  rename(se = `Std.Error`, estimate = Value, p = `p.value`) %>%
  mutate(upper95 = estimate + 1.96 * se, lower95 = estimate - 1.96 * se)

intercept_df %>%
  ggplot() +
  geom_point(aes(x = year, y = estimate), size = 3) +
  geom_linerange(aes(x = year, ymin = lower95, ymax = upper95), size = 1.2) +
  geom_hline(aes(yintercept = 50), alpha = 0.5, size = 1) +
  labs(x = "Election year", y = "Estimate of 2PP vote in average electorate") +
  coord_fixed(ratio = 0.2) +
  ylim(45.3, 54.7)
```

Since all socio-demographics have been standardized, the intercept in each model can be interpreted as the estimated two-party preferred vote for an "average" electorate. Figure \@ref(fig:plotintercept) shows that the baseline of party preference has varied over the elections, with the biggest swing occurring in the 2007 election where the mean electorate shifted more than five percentage points in favour of the Labor party. The dots represent the estimated 2PP value, and the lines indicate a 95% confidence interval providing a guide to the uncertainty in the estimate.

@@

```{r prepplot, echo = FALSE}
grid_visreg("Extractive", top = TRUE)
grid_visreg("DiffAddress")
grid_visreg("ManagerAdmin")
grid_visreg("Transformative")
grid_visreg("Incomes")
grid_visreg("Unemployment")
grid_visreg("MedianAge", top = TRUE)
grid_visreg("Judaism")
grid_visreg("OtherLanguage")
grid_visreg("OtherLanguage")
grid_visreg("BornAsia")
grid_visreg("Education")
grid_visreg("BornSEEuro")
grid_visreg("DeFacto")
```

Partial residual plots by election year for a selection of predictors. Linear model with 95\\% confidence bands overlaid. Most predictors have a positive relationship: the larger the value the more likely the electorate preferences the Coalition. The relationship is relatively robust over time, with the exception of Unemployment.

Several predictors have a negative relationship: with larger values indicating the electorate more likely preferences Labor. Most relationships are relatively stable over elections, except OtherLanguage and Education.

@@

@@

# From Emil

In terms of structure, start with a brief paragraph or two on what the research is, and what the reader can expect to find below.

Then, break the article into small sections for each of the factors that have an effect (a short paragraph or two for each factor). And it would be great to include examples of specific seats where the relationship was strong, or interesting for other reasons.

So the sections will be:

- Age
- Income
- Unemployment
- Industry and type of work
- Education
- Diversity
- Household mobility
- Relationships

An example of this structure can be seen here:
https://theconversation.com/confused-about-aged-care-in-the-home-these-10-charts-explain-how-it-works-113923

Questions on particular factors:

Incomes:
- Was this correlation stronger in 2016? (and increasingly influential?)

Household mobility
- In the report, you say: "“Having controlled for characteristics of house ownership and rental prices”, whis effect is somewhat surprising”. Why is this surprising to you? (I would have expected this to support Labor more)

Age
- Would it be possible to show how the correlation changes for different age brackets (ie. younger voters = more Labor, and this swings more to Liberal as the age brackets gets older)?
- If not, can you go into more detail specific age brackets? Eg. Is it the over-65s that skew Liberal?

Diversity
- Migrant population: Would it possible to break this out into particular groups? eg. Seats with higher Chinese population correlates with Liberal, seats with higher SEAsia pop correlates with Labor, etc?
- The same for languages?

### 2019-05-06 elections_conversation.tex
Updating on train

\documentclass[12pt,a4paper,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Who we are affects how we vote},
            pdfauthor={Rob J Hyndman and Di Cook},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[style=authoryear-comp]{biblatex}

@@

\usepackage[no-weekday]{eukdate}
\usepackage{sourcecodepro,sourceserifpro}
\usepackage{float,bm,setspace}
\setstretch{1.2}

@@

\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[htbp]
} {
    \endorigfigure
}

\let\origtable\table
\let\endorigtable\endtable
\renewenvironment{table}[1][2] {
    \expandafter\origtable\expandafter[htbp]
} {
    \endorigtable
}

@@

@@

Many of the socio-demographic variables have changing scales over the years. For example, inflation-adjusted median rental prices increased across almost all electorates, with median rent of 200 dollars per week placing an electorate in the 90th percentile in 2001, but only the 30th percentile in 2016. In order for socio-demographic effects to be comparable across years, all explanatory variables are standardized so they are comparable across years. By standardizing, each variable is reported as a relative measure compared to all other electorates in the same year.

There are dozens of socio-demographic variables available in the Censuses, with many variables representing similar information about an electorate. So we combined some variables to avoid redundant information. For example, our ``Incomes'' variable is a combination of median personal income, household income and family income. In this way, we reduced the data set to include 30 socio-demographic variables, listed below.

\begin{itemize}
\tightlist
\item
  ``AusCitizen''
\item
  ``BornAsia''
\item
  ``Born\_MidEast''
\item
  ``BornSEEuro''
\item
  ``Born\_UK''
\item
  ``BornElsewhere''
\item
  ``Buddhism''
\item
  ``Christianity''
\item
  ``CurrentlyStudying''
\item
  ``DeFacto''
\item
  ``DiffAddress''
\item
  ``Distributive''
\item
  ``Education''
\item
  ``Extractive''
\item
  ``FamHouseSize''
\item
  ``Incomes''
\item
  ``Indigenous''
\item
  ``Islam''
\item
  ``Judaism''
\item
  ``ManagerAdmin''
\item
  ``Married''
\item
  ``MedianAge''
\item
  ``NoReligion''
\item
  ``OneParentHouse''
\item
  ``OtherLanguage''
\item
  ``PropertyOwned''
\item
  ``RentLoanPrice''
\item
  ``SocialServ''
\item
  ``Transformative''
\item
  ``Unemployment''
\end{itemize}

Each election was modelled separately, to allow us to see any changes over time, and to account for changing electorate boundaries.

@@

{\centering \includegraphics[height=0.2\textheight,]{elections_conversation_files/figure-latex/plotintercept-1}

@@

\caption{Estimated intercept for each election, which represents the two-party preferred vote for an electorate with mean characteristics.}\label{fig:plotintercept}
\end{figure}

Since all socio-demographics have been standardized to have a mean of zero and a variance of one, the intercept in each model can be interpreted as the estimated two-party preferred vote for an electorate with mean characteristics\footnote{Mean of all variables aside from Judaism, Indigenous, Islam and Buddhism, where it assumes the mean of the log value.}. Figure \ref{fig:plotintercept} shows that the baseline of party preference has varied over the elections, with the biggest swing occurring in the 2007 election where the mean electorate shifted more than five percentage points in favour of the Labor party.

@@

{\centering \includegraphics{elections_conversation_files/figure-latex/partresplot1-1}

\caption{Partial residual plots by election year for a selection of predictors. Linear model with 95\% confidence bands overlaid. Most predictors have a positive relationship: the larger the value the more likely the electorate preferences the Coalition. The relationship is relatively robust over time, with the exception of Unemployment.}\label{fig:partresplot1}
\end{figure}

{\centering \includegraphics{elections_conversation_files/figure-latex/partresplot2-1}

\caption{Partial residual plots by election year for a selection of predictors. Linear model with 95\% confidence bands overlaid. Several predictors have a negative relationship: with larger values indicating the electorate more likely preferences Labor. Most relationships are relatively stable over elections, except OtherLanguage and Education.}\label{fig:partresplot2}
\end{figure}

@@

\hypertarget{a-note-on-similar-variables}{%
\subsubsection{A note on similar variables}\label{a-note-on-similar-variables}}

Many of the Census variables represent similar information, which is why factors were created and some variables were removed. However, some variables remain which are closely related. For example, an electorate's income level (via \texttt{Incomes}) is likely to be related to electoral unemployment and labor force participation (via \texttt{Unemployment}). In 2001, the coefficient estimate for \texttt{Unemployment} is negative but not significant, whilst the \texttt{Incomes} variables is significant. If the \texttt{Incomes} variable is removed from the model in 2001, \texttt{Unemployment} absorbs the negative effect, becoming significant (\(p = 0.0056\)).

@@

>>>>

\documentclass[11pt,a4paper,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Who we are affects how we vote},
            pdfauthor={Rob J Hyndman and Di Cook},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[style=authoryear-comp]{biblatex}

@@

\usepackage[no-weekday]{eukdate}
%\usepackage{sourceserifpro}
%\usepackage[scaled=0.86]{DejaVuSansMono}
\usepackage{float,bm,setspace}
\setstretch{1.2}

@@

@@

\begin{figure}[H]

@@

Many of the socio-demographic variables have changing scales over the years. For example, inflation-adjusted median rental prices increased across almost all electorates, with median rent of 200 dollars per week placing an electorate in the 90th percentile in 2001, but only the 30th percentile in 2016. In order for socio-demographic effects to be comparable across years, all socio-demographic variables were standardized.

There are dozens of socio-demographic variables available in the Censuses, with many variables representing similar information about an electorate. So we combined some variables to avoid redundant information. For example, our ``Incomes'' variable is a combination of median personal income, household income and family income.

Each election was modelled separately, to allow us to see any changes over time, and to account for changing electorate boundaries. In this article, we highlight the variables with the strongest relationship to the two-party preferred vote, or which have had substantial changes over time. The full analysis is available at \url{https://robjhyndman.com/publications/elections/}.

@@

\begin{figure}[H]

{\centering \includegraphics{elections_conversation_files/figure-latex/plotintercept-1}

@@

\caption{Estimated intercept for each election, which represents the two-party preferred vote for an electorate with average characteristics.}\label{fig:plotintercept}
\end{figure}

Since all socio-demographics have been standardized, the intercept in each model can be interpreted as the estimated two-party preferred vote for an ``average'' electorate. Figure \ref{fig:plotintercept} shows that the baseline of party preference has varied over the elections, with the biggest swing occurring in the 2007 election where the mean electorate shifted more than five percentage points in favour of the Labor party. The dots represent the estimated 2PP value, and the lines indicate a 95\% confidence interval providing a guide to the uncertainty in the estimate.

@@

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-1} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-2} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-3} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-4} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-5} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-6} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-7} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-8} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-9} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-10} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-11} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-12} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-13} \end{center}

\begin{center}\includegraphics{elections_conversation_files/figure-latex/prepplot-14} \end{center}

Partial residual plots by election year for a selection of predictors. Linear model with 95\textbackslash{}\% confidence bands overlaid. Most predictors have a positive relationship: the larger the value the more likely the electorate preferences the Coalition. The relationship is relatively robust over time, with the exception of Unemployment.

Several predictors have a negative relationship: with larger values indicating the electorate more likely preferences Labor. Most relationships are relatively stable over elections, except OtherLanguage and Education.

@@

@@

\hypertarget{from-emil}{%
\section{From Emil}\label{from-emil}}

In terms of structure, start with a brief paragraph or two on what the research is, and what the reader can expect to find below.

Then, break the article into small sections for each of the factors that have an effect (a short paragraph or two for each factor). And it would be great to include examples of specific seats where the relationship was strong, or interesting for other reasons.

So the sections will be:

\begin{itemize}
\tightlist
\item
  Age
\item
  Income
\item
  Unemployment
\item
  Industry and type of work
\item
  Education
\item
  Diversity
\item
  Household mobility
\item
  Relationships
\end{itemize}

An example of this structure can be seen here:
\url{https://theconversation.com/confused-about-aged-care-in-the-home-these-10-charts-explain-how-it-works-113923}

Questions on particular factors:

Incomes:
- Was this correlation stronger in 2016? (and increasingly influential?)

Household mobility
- In the report, you say: ````Having controlled for characteristics of house ownership and rental prices'', whis effect is somewhat surprising''. Why is this surprising to you? (I would have expected this to support Labor more)

Age
- Would it be possible to show how the correlation changes for different age brackets (ie. younger voters = more Labor, and this swings more to Liberal as the age brackets gets older)?
- If not, can you go into more detail specific age brackets? Eg. Is it the over-65s that skew Liberal?

Diversity
- Migrant population: Would it possible to break this out into particular groups? eg. Seats with higher Chinese population correlates with Liberal, seats with higher SEAsia pop correlates with Labor, etc?
- The same for languages?
